Model LF

### 2022-10-11 Estimation.Rmd
Changes to productivity function

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3) +  L(TSDELTA(s_h),c(1:4))+  L(TSDELTALOG(mean_dp_regul),0)  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1))

@@

>>>>

d_2019q34=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2019,3), dummy_end = c(2019,4),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2016_end=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2016,1), dummy_end = c(2020,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3) +  L(TSDELTA(s_h),c(1:2,4))  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1) + L(log(mean_dp_regul),1))

@@

```{r}
res_reg_kuld_done=residuals(reg_prod)
shapiro.test(res_reg_kuld_done)
```
